Reliability-Aware Hierarchical Learning for Chagas Detection from Electrocardiogram under Expert Label Scarcity

### 2025-09-25 contents/abstract.tex
fix errors
update final test results

Results: On the hidden validation set, our method received a Challenge score of 0.245 (rank 179~/~364). In cross-validation on the public training data, our approach achieved a Challenge score of 0.451.

Conclusion: The proposed method shows effective performance for ECG-based Chagas screening, and highlights potential for improving detection accuracy and reliability in resource-limited scenarios.

>>>>

Results: On the hidden validation set, our method received a Challenge score of 0.163 (rank 32~/~40). In cross-validation on the public training data, our approach achieved a Challenge score of 0.451.

Conclusion: The proposed method demonstrates effective performance for ECG-based Chagas screening, highlighting its potential for improving detection accuracy and reliability in resource-limited scenarios.

### 2025-09-25 contents/discussions.tex
update final test results

The hidden validation Challenge score presented in Table~\ref{tab:scores} indicates that our proposed method is effective for Chagas screening from ECGs, albeit with substantial room for improvement. The result demonstrates our model's ability to learn diagnostically relevant features from ECGs for this task under scarce and noisy supervision. This is achieved through reliability-aware label smoothing, which incorporates both label provenance and reliability instead of treating all positive labels uniformly. Together with the asymmetric loss and strategic upsampling, these results indicate that explicitly modeling label reliability helps stabilize the learning process more effectively than introducing additional architectural complexity. Overall, our approach offers a scalable and resource-efficient solution and aligns well with the Challenge's objective of identifying high-risk individuals under limited serological testing capacity.

>>>>

The Challenge scores presented in Table~\ref{tab:scores} indicates that our proposed method is effective for Chagas screening from ECGs, albeit with substantial room for improvement. The result demonstrates our model's ability to learn diagnostically relevant features from ECGs for this task under scarce and noisy supervision. This is achieved through reliability-aware label smoothing, which incorporates both label provenance and reliability instead of treating all positive labels uniformly. Together with the asymmetric loss and strategic upsampling, these results indicate that explicitly modeling label reliability helps stabilize the learning process more effectively than introducing additional architectural complexity. Overall, our approach offers a scalable and resource-efficient solution and aligns well with the Challenge's objective of identifying high-risk individuals under limited serological testing capacity.

### 2025-09-25 poster.tex
update final test results

\begin{center}
\begin{tabular}{r|r|r|r}
Internal hold-out (mean±std) & Hidden validation & Rank & Test \\
\hline
$0.451 \pm 0.005$ & 0.245 & 179/364 & TBA \\
\hline
\end{tabular}
\end{center}
\vspace{-1ex}
The rankings are based on the hidden validation set. Results on the public training data (more specifically, the hold-out subset) are also provided for reference.

>>>>

\begin{center}
\begin{tabular}{r|r|r|r}
Internal hold-out (mean±std) & Hidden validation & Test & Rank \\
\hline
$0.451 \pm 0.005$ & 0.245 & 0.163 & 32/40 \\
\hline
\end{tabular}
\end{center}
\vspace{-1ex}
The rankings are based on the hidden test set. Results on the public training data (more specifically, the hold-out subset) are also provided for reference.
